Interactive Visualization of Hierarchically Structured Data

### 2017-03-23 treelapse.Rmd
For the rest, edit in tex

---
standalone: true
documentclass: article
fontsize: 12pt
output:
  bookdown::pdf_book:
    keep_tex: yes
    toc: false
    includes:
      in_header: preamble.tex
      before_body: before_body.tex
bibliography: ["bibliography.bib"]
biblio-style: "agsm"
link-citations: yes
---

>>>>

---
standalone: true
documentclass: article
fontsize: 12pt
output:
  bookdown::pdf_book:
    keep_tex: yes
    toc: false
    includes:
      in_header: preamble.tex
      before_body: before_body.tex
bibliography: ["bibliography.bib"]
biblio-style: "agsm"
link-citations: yes
number-sections: false
---
